Testable normative theories

### 2020-05-20 simple.tex
\zar unnecessary, it seems

\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
with $\zar \in \allargs, {\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$. Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.

>>>>

\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$. Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.
